\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
remove redundant word

%%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
To exchange geometry descriptions between software packages the Geometry Description Markup Language (GDML) was developed~\cite{GDML}. 
GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
GDML format and it is commonly used as an exchange format for Geant4 geometries.

>>>>

%%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
To exchange geometry descriptions between software packages the Geometry Description Markup Language (GDML) was developed~\cite{GDML}. 
GDML is an XML-based description of Geant4 geometry. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
GDML and it is commonly used as an exchange format for Geant4 geometries.
